---
title: "R Notebook"
output: html_notebook
---

# Selected subset A
selected_a - includes cells [Myofibroblast, vasa recta endothelium, Peritubular capillary endothelium]; trimmed to 1000 cells; with the original embedding
selected_a_2 - the same as selected_a, but with the new embedding
## Select and Transform Data
```{r}
unique(kidney$celltype)
length(unique(kidney$celltype))
```

```{r}
to_select <- c("Myofibroblast", "Descending vasa recta endothelium", "Peritubular capillary endothelium 2", "Peritubular capillary endothelium 1", "Ascending vasa recta endothelium")
selected_meta <- is.element(kidney$celltype, to_select)
kidney <- AddMetaData(kidney, metadata=selected_meta, col.name="selected_ENDO")
selected_a <- subset(x = kidney, subset = selected_ENDO == TRUE)
ncol(selected_a)
selected_a <- selected_a[,colnames(selected_a)[1:1000]]
ncol(selected_a)
```

```{r}
selected_a_2 <- SCTransform(selected_a, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
selected_a_2 <- RunPCA(selected_a_2, features = VariableFeatures(object = selected_a_2))
```

```{r}
selected_a_2 <- RunUMAP(selected_a_2, dims = 1:30, verbose = FALSE)
selected_a_2 <- FindNeighbors(selected_a_2, dims = 1:30, verbose = FALSE)
selected_a_2 <- FindClusters(selected_a_2, resolution = 0.1, verbose = FALSE)
selected_a_2 <- RunTSNE(selected_a_2)
```

```{r}
DimPlot(selected_a, label = TRUE, label.size = 3, group.by="seurat_clusters") + NoLegend()
DimPlot(selected_a, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

```{r}
my_cols <- c('#003366','#00cc99','#cc9900','#ff0066','#6699ff','#E6C122','#000195','#B95FBB','#28CECA','#ff9a36','#2FF18B','#aeadb3','#CCB1F1','#D4D915','#A4DFF2','#4B4BF7')
DimPlot(selected_a_2, label = TRUE, label.size = 3, group.by="seurat_clusters") + NoLegend()
DimPlot(selected_a_2, reduction = "umap", group.by="celltype",repel = TRUE, label = FALSE, label.size = 3, cols=my_cols[1:5]) #+ NoLegend()
```

## Generate SNN graph
```{r}
n = ncol(selected_a_2)
dim(selected_a_2)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 20 #30
k = 8
coff = 0.1 #0.067 
ord = 8

selected_a_2 <- FindNeighbors(selected_a_2, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff)

selected_a_2_snn_temp <- selected_a_2@graphs[["SCT_snn"]]

dim(selected_a_2_snn_temp)
selected_a_2_snn <- selected_a_2_snn_temp - diag(nrow=n, ncol=n)

library(proxyC)
 
# ------- limitation of nodes degrees SYMMETRICS-------
print(sum(colZeros(selected_a_2_snn)))
for (i in 1:n){
  to_delete <- order(selected_a_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_a_2_snn[,i][to_delete] <- integer(n-ord)
  selected_a_2_snn[i,][to_delete] <- integer(n-ord)
}
print(sum(colZeros(selected_a_2_snn)))
```

```{python}
id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

G = nx.from_numpy_matrix(r.selected_a_2_snn)
G.number_of_nodes()

file_name = ''.join(["../../graphs/R_generated/kidney_endo/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_TEST.gexf"])
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/R_generated/kidney_endo/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_TEST.png"])
plt.savefig(file_name, bbox_inches='tight')
```

## Optional stage for removing disconnected subsets and SNN graph re-evaluation; graph tuning by shared edges enhancement
```{python}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

def disconnected_components(G):
    lengths  = [len(c) for c in sorted(nx.connected_components(G), key=len, reverse=True)]
    print(lengths)
    S = [G.subgraph(c).copy() for c in nx.connected_components(G)]
    for s in S:
        print(len(s.nodes()))
        if len(s.nodes()) > 15:
            subindex = 0
            for n in s.nodes():
                G.nodes(data=True)[n]["subindex"] = subindex
                G.nodes(data=True)[n]["valid"] = 1
                subindex = subindex + 1            
        else:
            for n in s.nodes():
                G.nodes(data=True)[n]["valid"] = 0
    return G, S, lengths

  
G = nx.from_numpy_matrix(r.selected_a_2_snn)

G, S, lengths = disconnected_components(G)
print(lengths)
G = S[0]
G.number_of_nodes()

to_remove=[list(graph.nodes) for graph in S[1:]]
to_remove_flat=[item for sublist in to_remove for item in sublist]
print("to be removed: ", end="")
print(to_remove_flat)
G.remove_nodes_from(to_remove_flat)

list(nx.isolates(G))
```

```{r, eval=FALSE}
selected_a_2_backup <- selected_a_2
selected_a_2 <- selected_a_2_backup
```

```{r, eval=False}
toRemove <- py$to_remove_flat
print(length(colnames(selected_a_2)))
      
toRemove_col_name <- colnames(selected_a_2)[as.vector(toRemove)]

selected_a_2_filtered <- selected_a_2[,!colnames(selected_a_2) %in% toRemove_col_name]

length(colnames(selected_a_2_filtered)) 

selected_a_2 <- selected_a_2_filtered

n = ncol(selected_a_2)
dim(selected_a_2)

coff = 0.0001

selected_a_2 <- FindNeighbors(selected_a_2, dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff)

selected_a_2_snn_temp <- selected_a_2@graphs[["SCT_snn"]]

dim(selected_a_2_snn_temp)
selected_a_2_snn <- selected_a_2_snn_temp - diag(nrow=n, ncol=n)
```

```{r, eval=FALSE}
isSymmetric(as.matrix(selected_a_2_snn))

# ------- Enhance shared edges (may want to repeat multiple times) -------
library(Matrix)

# Method 2 (better)
mutual = matrix(0,n,n)

for (i in 1:n){
    mutual[i,] <- selected_a_2_snn[i,] & selected_a_2_snn[,i] 
}
nnzero(mutual)

selected_a_2_snn_old <- selected_a_2_snn
for (i in 1:n){
    selected_a_2_snn[i,] <- selected_a_2_snn_old[i,]+mutual[,i]
}
```

## Plot and save graphs 

```{python}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["../../graphs/R_generated/kidney_endo/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".gexf"])

G = nx.from_numpy_matrix(r.selected_a_2_snn)
nodes = G.nodes
print("CQM nomber of nodes: ", G.number_of_nodes())
edges = G.edges
print("CQM nomber of edges: ", G.number_of_edges())
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/R_generated/kidney_endo/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".png"])
plt.savefig(file_name, bbox_inches='tight')
```

```{r}
knitr::include_graphics(py$file_name)
```

## Functions
```{r, eval=False}
datatransformation <- function(fdata) {
  fdata2 <- SCTransform(fdata, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
  fdata2 <- RunPCA(fdata2, features = VariableFeatures(object = fdata))
  fdata2 <- RunUMAP(fdata2, dims = 1:30, verbose = FALSE)
  fdata2 <- FindNeighbors(fdata2, dims = 1:30, verbose = FALSE)
  fdata2 <- FindClusters(fdata2, resolution = 0.1, verbose = FALSE)
  return(fdata2)
}
```

```{r, eval=False}
generatesnn <- function(fdata) {
  n = ncol(fdata)
  dim(fdata)
  
  type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
  id_type = 2
  dim = 30
  k = 10
  coff = 0.067 #1/15
  ord = 15
  
  fdata <- FindNeighbors(fdata, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff)
  
  fdata_snn_temp <- fdata@graphs[["SCT_snn"]]
  
  dim(fdata_snn_temp)
  fdata_snn <- fdata_snn_temp - diag(nrow=n, ncol=n)
  return(fdata_snn)
}
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees SYMMETRICS-------
limitnodes <- function(fdata) {
  print(sum(colZeros(fdata)))
  for (i in 1:n){
    to_delete <- order(fdata[,i], decreasing = TRUE)[seq(ord+1,n,1)]
    fdata[,i][to_delete] <- integer(n-ord)
    fdata[i,][to_delete] <- integer(n-ord)
  }
  print(sum(colZeros(fdata)))
}
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees UNSYMMETRIC -------
print(sum(colZeros(selected_a_2_snn)))
for (i in 1:n){
  to_delete <- order(selected_a_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_a_2_snn[,i][to_delete] <- integer(n-ord)
}
print(sum(colZeros(selected_a_2_snn)))
```

```{r, eval=FALSE}
# ------- Enhance shared edges (may want to repeat multiple times) -------
library(Matrix)

# Method 1
selected_a_2_snn_old <- selected_a_2_snn
for (i in 1:n){
    selected_a_2_snn[i,] <- selected_a_2_snn_old[i,]+selected_a_2_snn_old[,i]
}
```

```{python, eval=False}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

plotsavegraphs <- function(name, fdata) {

  id_type, type = int(r.id_type)-1, r.type
  n = int(r.n)
  k = int(r.k)
  ord = int(r.ord)
  dim = int(r.dim)

  file_name = ''.join(["../../graphs/R_generated/kidney_endo/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_bench.gexf"])

  G = nx.from_numpy_matrix(r.selected_a_2_snn)
  nx.write_gexf(G, file_name)

  G = nx.read_gexf(file_name)
  pos = nx.spring_layout(G)
  plt.cla()
  nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
  nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

  file_name = ''.join(["../../graphs/R_generated/kidney_endo/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_bench.png"])
  plt.savefig(file_name, bbox_inches='tight')
}
```

