---
title: "R Notebook"
output: html_notebook
---

---
title: "R Notebook"
output: html_notebook
---
takes QA clustered graph:   QA_clusters
takes Seurat object:        selected_a              (from "Kidney_data" notebook, original graph)
takes Seurat object:        selected_a_2            (from "Kidney_data" notebook, original graph)
input data:                 ../../dataIn/kidney/MNP/    copied from   ./graphs_multi_samples/
output data:                ../../output/   and   ../../output/multi_eng/
# Libraries
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(Seurat)
library(ggplot2)
library(bspec)
library(sctransform)
library(cowplot)
library(gridExtra)
library(dplyr)
library(patchwork)
library(sctransform)
library(glmGamPoi)
```

# Compare clusters
## Import QA clusters (only the first sample)
```{r setup}
library(reticulate)
virtualenv_create("scrna_proj")
# py_install(c("networkx","matplotlib"), envname = "scrna_proj")
use_virtualenv("scrna_proj")
```

```{python}
import networkx as nx

dataset = "MNP/"
ex_number = "1"
QA_output_name = "sample_number" + ex_number + ".gexf"
QA_clusters = nx.read_gexf(''.join(["../../dataIn/kidney/", dataset, QA_output_name]))

# ------- CHOSE THE CORRECT OPTION BASED ON THE EXPORTED FORMAT -------
# colors = [y[sorted(y.keys())[-1]] for x,y in sorted(QA_clusters.nodes(data=True))]
colors = [y[sorted(y.keys())[-1]] for x,y in QA_clusters.nodes(data=True)]
len(colors)
```

## Merge Clusters MetaData
```{r}
ex_number <- py$ex_number

my_cols <- c('#003366','#00cc99','#cc9900','#ff0066','#6699ff','#E6C122','#000195','#B95FBB','#28CECA','#ff9a36'
             ,'#2FF18B','#aeadb3','#CCB1F1','#D4D915','#A4DFF2','#4B4BF7')

colors = py$colors
colors = unlist(colors)
selected_a <- AddMetaData(selected_a, metadata=colors, col.name="QA")
DimPlot(selected_a, reduction = "pca", group.by="QA", cols=my_cols[1:5]) + NoLegend()
```

```{r}
colors = py$colors
colors = unlist(colors)
selected_a_2<- AddMetaData(selected_a_2, metadata=colors, col.name="QA")

DimPlot(selected_a_2, reduction = "pca", group.by="QA", cols=my_cols[1:5], raster.dpi = c(512, 512)) + NoLegend()
# ggsave(paste("../../output/PCA.png"), width = 5, height = 5) 
```

```{r}
png(file= paste("../../output/selected_a_seurat", ex_number, ".png"))
DimPlot(selected_a, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
dev.off()

png(file=paste("../../output/selected_a_QA", ex_number, ".png"))
DimPlot(selected_a, reduction = "umap", group.by="QA") # + NoLegend()
dev.off()

png(file=paste("../../output/selected_a_celltypes", ex_number, ".png"))
DimPlot(selected_a, reduction = "umap", group.by="celltype") # + NoLegend()
dev.off()

# par(mfrow = c(1, 2))
DimPlot(selected_a, reduction = "umap", group.by="QA", cols=my_cols[1:5]) # + NoLegend()
DimPlot(selected_a, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
DimPlot(selected_a, reduction = "umap", group.by="celltype", cols=my_cols[1:5]) # + NoLegend()
```

```{r}
png(file=paste("../../output/selected_a_2_seurat", ex_number, ".png"))
DimPlot(selected_a_2, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
dev.off()

png(file=paste("../../output/selected_a_2_QA", ex_number, ".png"))
DimPlot(selected_a_2, reduction = "umap", group.by="QA") # + NoLegend()
dev.off()

png(file=paste("../../output/selected_a_2_celltypes", ex_number, ".png"))
DimPlot(selected_a_2, reduction = "umap", group.by="celltype") # + NoLegend()
dev.off()

# par(mfrow = c(1, 2))
DimPlot(selected_a_2, reduction = "umap", group.by="QA", cols=my_cols[1:5]) # + NoLegend()
DimPlot(selected_a_2, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
DimPlot(selected_a_2, reduction = "umap", group.by="celltype", cols=my_cols[1:5]) # + NoLegend()
```


## Plot UMAP for Multiple Energies
```{python}
colors = []
for i in range(0,15):
  ex_number = str(i)
  QA_output_name = "sample_number" + ex_number + ".gexf"
  QA_clusters = nx.read_gexf(''.join(["../../dataIn/kidney/", dataset, QA_output_name]))
  color = [y[sorted(y.keys())[-1]] for x,y in QA_clusters.nodes(data=True)]
  colors.append(color)

```

```{r}
colors <- py$colors
graph_colors <- my_cols[1:5]
graph_colors_ord <- graph_colors
size <- length(unlist(colors[1]))
fig_size <- 5

for (i in c(1:15)) {
  print(i)
  color <- colors[i]
  color <- unlist(color)
  color <- color + 1
  
  ord <- order(table(color), decreasing = TRUE)
  color_new <- color
  for (j in c(1:size)){
    color_new[j] <- switch(color[j], which(ord==1), which(ord==2), which(ord==3), which(ord==4), which(ord==5))
  }
  
  selected_a_2 <- AddMetaData(selected_a_2, metadata=color_new, col.name="QA")
  
  DimPlot(selected_a_2, reduction = "umap", group.by="QA", cols=graph_colors) + NoLegend()
  ggsave(paste("../../output/multi_eng/selected_a_2_QA_", as.character(i), ".png", sep = ""), width = fig_size, height = fig_size)
}

color = as.numeric(selected_a_2$seurat_clusters)
ord <- order(table(color), decreasing = TRUE)
color_new <- color
for (j in c(1:size)){
  color_new[j] <- switch(color[j], which(ord==1), which(ord==2), which(ord==3), which(ord==4), which(ord==5))
}
selected_a_2 <- AddMetaData(selected_a_2, metadata=color_new, col.name="seurat_clusters")
DimPlot(selected_a_2, reduction = "umap", group.by="seurat_clusters", cols=graph_colors) # + NoLegend()
ggsave(paste("../../output/multi_eng/selected_a_2_seurat.png"), width = fig_size, height = fig_size)

cell_types = selected_a_2$celltype
for (i in 1:size) {
  color_new[i] <- switch(cell_types[i], "MNP-a/classical monocyte derived"=5, "MNP-b/non-classical monocyte derived"=1, "MNP-d/Tissue macrophage"=3, "MNP-c/dendritic cell"=2, "Neutrophil"=4)
}
selected_a_2 <- AddMetaData(selected_a_2, metadata=color_new, col.name="Cell_types_ground_truth")
DimPlot(selected_a_2, reduction = "umap", group.by="Cell_types_ground_truth", cols=graph_colors) # + NoLegend() #, raster.dpi=c()
ggsave(paste("../../output/multi_eng/selected_a_2_celltypes.png"), width = 5, height = 5)
```

```{r}
MyLabb <- c("MNP-a/classical monocyte derived", "MNP-b/non-classical monocyte derived", "MNP-d/Tissue macrophage", "MNP-c/dendritic cell", "Neutrophil")
MyLab <- c(MyLabb[1], MyLabb[5], MyLabb[2], MyLabb[3], MyLabb[4])
  
data <- data.frame(x = 1:5,                        # Create example data
                   y = 1:5)
                        
library("ggplot2")     
library("grid")                     
library("gridExtra")        
library("cowplot")
png("../../output/multi_eng/legend.png",width = 1500, height = 100, pointsize=30)
ggp <- ggplot(data, aes(x, y, color = MyLab)) + labs(colour =" ") +
  geom_point(size = 10) + scale_color_manual(labels = MyLab, values=graph_colors_2) + guides(colour = guide_legend(nrow = 2)) + theme_bw() +
  theme(legend.text=element_text(size=rel(2)))
ggp
ggp_legend <- get_legend(ggp)
grid.newpage()                                     # Draw empty plot window
grid.draw(ggp_legend)
dev.off()
```
## Plot only selected sample

```{r}
i = 8
print(i)
color <- colors[i]
color <- unlist(color)
color <- color + 1

ord <- order(table(color), decreasing = TRUE)
color_new <- color
for (j in c(1:size)){
  color_new[j] <- switch(color[j], which(ord==1), which(ord==2), which(ord==3), which(ord==4), which(ord==5))
}

selected_a_2 <- AddMetaData(selected_a_2, metadata=color_new, col.name="QA")

graph_colors_2 <- graph_colors
graph_colors_2[3] <- graph_colors[5]
graph_colors_2[5] <- graph_colors[3]

DimPlot(selected_a_2, reduction = "umap", group.by="QA", cols=graph_colors_2) + NoLegend()
ggsave(paste("../../output/multi_eng/selected_a_2_QA_", as.character(i), ".png", sep = ""), width = fig_size, height = fig_size)
```

