---
title: "R Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
Processes Kidney dataset
Selects and processes: selected_b(old embedding), selected_b_2(new embedding), selected_b_2_pruned 
# Libraries
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(Seurat)
library(ggplot2)
library(bspec)
library(sctransform)
library(cowplot)
library(gridExtra)
library(dplyr)
library(patchwork)
library(sctransform)
library(glmGamPoi)
library(SeuratDisk)
library("parallel")
```
# Whole Dataset
kidney - whole dataset, 10605 samples
## Clean Data
```{r}
# ------- use previously created Seurat object -------
kidney <- readRDS(file = "../../data/kidney_demo_stewart.rds")
```

```{r}
kidney[["percent.mt"]] <- PercentageFeatureSet(kidney, pattern = "^MT-")

kidney <- subset(kidney, subset = nFeature_RNA > 203 & nFeature_RNA < 7000 & nCount_RNA > 254 & nCount_RNA < 40000 & percent.mt < 20) 
```

## Transform Data
```{r}
kidney <- SCTransform(kidney, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
kidney <- RunPCA(kidney, features = VariableFeatures(object = kidney))
```

```{r}
kidney <- RunUMAP(kidney, reduction = "pca", dims = 1:10)
DimPlot(kidney, reduction = "umap", group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) + NoLegend()
```

# Select Data for subsampling
selected_b -- with old (whole dataset) embedding, selected cells: NK, NKT, CD4, CD8 and Mast cells  
selected_b_2-- with new (selected dataset) embedding
selected_b_2_pruned -- QA pruning results

## Transform Data
```{r}
to_select <- c("NK cell", "NKT cell", "CD8 T cell", "CD4 T cell", "Mast cell")
selected_meta <- is.element(kidney$celltype, to_select)
kidney <- AddMetaData(kidney, metadata=selected_meta, col.name="selected")
selected_b <- subset(x = kidney, subset = selected == TRUE)
ncol(selected_b)
DimPlot(selected_b, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

```{r}
selected_b_2 <- SCTransform(selected_b, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
selected_b_2 <- RunPCA(selected_b_2, features = VariableFeatures(object = selected_b_2))
```

```{r}
n = ncol(selected_b_2)
dim(selected_b_2)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 30
k = 10
coff = 0.067 #1/15
ord = 10

selected_b_2 <- FindNeighbors(selected_b_2, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff, verbose = FALSE)

selected_b_2 <- FindClusters(selected_b_2, resolution = 0.04, verbose = FALSE)
```

```{r}
selected_b_2 <- RunUMAP(selected_b_2, dims = 1:30, verbose = FALSE)
```

```{r}
DimPlot(selected_b_2, label = TRUE, label.size = 3, group.by="seurat_clusters") #+ NoLegend()
DimPlot(selected_b_2, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

## Generate SNN graph
```{r, eval=FALSE}
selected_b_2_snn_temp <- selected_b_2@graphs[["SCT_snn"]]

dim(selected_b_2_snn_temp)
selected_b_2_snn <- (selected_b_2_snn_temp - diag(nrow=n, ncol=n))
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees SYMMETRICS-------
for (i in 1:n){
  to_delete <- order(selected_b_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_b_2_snn[,i][to_delete] <- integer(n-ord)
  selected_b_2_snn[i,][to_delete] <- integer(n-ord)
}
```

## Plot and save graphs 
```{r setup}
library(reticulate)
virtualenv_create("scrna_proj")
# py_install(c("networkx","matplotlib"), envname = "scrna_proj")
use_virtualenv("scrna_proj")
```

```{python, eval=FALSE}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_selected_to_prune.gexf"])

G = nx.from_numpy_matrix(r.selected_b_2_snn)
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_selected_to_prune.png"])
plt.savefig(file_name, bbox_inches='tight')
```


#Subsampling
## import QA results
```{python}
# IMPORT GRAPH SUBSAMPLING (indicated by attribute "label1" : 1)
import networkx as nx
# QA_output_name = "prun_results/2901_pru_graph_snn_k10_dim30_trimmed_15v3.gexf" # 942 nodes
QA_output_name = "prun_results/2901_pru_graph_snn_k10_dim30_trimmed_15_pruned_5.gexf" # 777 nodes

QA_prune = nx.read_gexf(''.join(["../../dataIn/kidney/", QA_output_name]))
```

```{python}
# GET THE PRUNED NODES
# ------- CHOSE THE CORRECT OPTION BASED ON THE EXPORTED FORMAT -------
pruned = [y[sorted(y.keys())[-1]] for x,y in sorted(QA_prune.nodes(data=True))]
pruned = [y[sorted(y.keys())[-1]] for x,y in QA_prune.nodes(data=True)]
```


## Merge MetaData
```{r}
pruned = py$pruned
selected_b_2 <- AddMetaData(selected_b_2, metadata=pruned, col.name="QA_pruning")
```

```{r}
DimPlot(selected_b_2, reduction = "umap", group.by="QA_pruning")
```
```{r}
# PRUNIGN THE GRAPH
pruned = py$pruned
pruned = unlist(pruned)

selected_b_2_pruned <- selected_b_2[,!!pruned]

dim(selected_b_2_pruned@assays$RNA)
```

## Create new graph

```{r}
# PRUNIGN THE GRAPH
pruned = py$pruned
pruned = unlist(pruned)

selected_b_2_pruned <- selected_b_2[,!!pruned]

# ------- Process pruned data set -------
selected_b_2_pruned <- SCTransform(selected_b_2_pruned, method = "glmGamPoi", vars.to.regress = "percent.mt", verbose = FALSE)
selected_b_2_pruned <- RunPCA(selected_b_2_pruned, features = VariableFeatures(object = selected_b_2_pruned))

n = ncol(selected_b_2_pruned)
dim(selected_b_2_pruned)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 30
k = 10
coff = 0 #1/15
ord = 15

selected_b_2_pruned <- FindNeighbors(selected_b_2_pruned, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE) #prune.SNN=coff
```

```{r, eval=FALSE}
selected_b_2_pruned_snn <- selected_b_2_pruned@graphs[["SCT_snn"]]

dim(selected_b_2_pruned_snn)
selected_b_2_pruned_snn_temp <- selected_b_2_pruned_snn
selected_b_2_pruned_snn <- (selected_b_2_pruned_snn_temp - diag(nrow=n, ncol=n))
remove(selected_b_2_pruned_snn_temp)
# selected_b_2_pruned_snn <- round(selected_b_2_pruned_snn, digits=2)
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees SYMMETRICS-------
for (i in 1:n){
  to_delete <- order(selected_b_2_pruned_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_b_2_pruned_snn[,i][to_delete] <- integer(n-ord)
  selected_b_2_pruned_snn[i,][to_delete] <- integer(n-ord)
}
```

```{r, eval=FALSE}
# ------- limitation of nodes degrees UNSYMMETRIC -------
for (i in 1:n){
  to_delete <- order(selected_b_2_pruned_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_b_2_pruned_snn[,i][to_delete] <- integer(n-ord)
}
```

```{r, eval=FALSE}
# ------- Enhance shared edges (may want to repeat multiple times) -------
library(Matrix)

# Method 1
selected_b_2_pruned_snn_old <- selected_b_2_pruned_snn
for (i in 1:n){
    selected_b_2_pruned_snn[i,] <- selected_b_2_pruned_snn_old[i,]+selected_b_2_pruned_snn_old[,i]
}

# Method 2
mutual = matrix(0,n,n)

for (i in 1:n){
    mutual[i,] <- selected_b_2_pruned_snn[i,] & selected_b_2_pruned_snn[,i] 
}
nnzero(mutual)

selected_b_2_pruned_snn_old <- selected_b_2_pruned_snn
for (i in 1:n){
    selected_b_2_pruned_snn[i,] <- selected_b_2_pruned_snn_old[i,]+mutual[,i]
}
```

## Plot and save graphs
```{python, eval=FALSE}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["../../graphs/kidney/", str(n), "_pru_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".gexf"])

G = nx.from_numpy_matrix(r.selected_b_2_pruned_snn)
nx.write_gexf(G, file_name)
G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/kidney/", str(n), "_pru_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), ".png"])
plt.savefig(file_name, bbox_inches='tight')
```

```{r, eval=FALSE}
knitr::include_graphics(py$file_name)
```

