---
title: "R Notebook"
output: html_notebook
---

# Selected subset B
selected_a - includes cells ["MNP-a/classical monocyte derived", "MNP-b/non-classical monocyte derived", "MNP-d/Tissue macrophage", "MNP-c/dendritic cell", "Neutrophil"] with the original embedding
selected_a_2 - the same as selected_a, but with a new embedding
output in --> ../../graphs/kidney/MNP/
# Libraries
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(Seurat)
library(ggplot2)
library(bspec)
library(sctransform)
library(cowplot)
library(gridExtra)
library(dplyr)
library(patchwork)
library(sctransform)
library(glmGamPoi)
library(SeuratDisk)
library("parallel")
```

## Select and Transform Data
```{r}
unique(kidney$celltype)
length(unique(kidney$celltype))
```


```{r}
to_select <- c("MNP-a/classical monocyte derived", "MNP-b/non-classical monocyte derived", "MNP-d/Tissue macrophage", "MNP-c/dendritic cell", "Neutrophil")
selected_meta <- is.element(kidney$celltype, to_select)
kidney <- AddMetaData(kidney, metadata=selected_meta, col.name="selected_MNP")
selected_a <- subset(x = kidney, subset = selected_MNP == TRUE)
ncol(selected_a)
```

```{r}
selected_a_2 <- SCTransform(selected_a, vars.to.regress = "percent.mt", method = "glmGamPoi", verbose = FALSE)
selected_a_2 <- RunPCA(selected_a_2, features = VariableFeatures(object = selected_a_2))
DimPlot(selected_a_2, reduction = "pca", group.by="celltype") + NoLegend()
```

```{r}
selected_a_2 <- RunUMAP(selected_a_2, dims = 1:30, verbose = FALSE)
selected_a_2 <- FindNeighbors(selected_a_2, dims = 1:30, verbose = FALSE)
selected_a_2 <- FindClusters(selected_a_2, resolution = 0.1, verbose = FALSE)
```

```{r}
DimPlot(selected_a, label = TRUE, label.size = 3, group.by="seurat_clusters") + NoLegend()
DimPlot(selected_a, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

```{r}
DimPlot(selected_a_2, label = TRUE, label.size = 3, group.by="seurat_clusters") + NoLegend()
DimPlot(selected_a_2, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

## Generate SNN graph
```{r}
n = ncol(selected_a_2)
dim(selected_a_2)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 40
k = 20
coff = 0.1 #1/15
ord = 20

selected_a_2 <- FindNeighbors(selected_a_2, reduction = "pca", dims = 1:dim, k.param=k, compute.SNN=TRUE, prune.SNN=coff)

selected_a_2_snn_temp <- selected_a_2@graphs[["SCT_snn"]]

dim(selected_a_2_snn_temp)
selected_a_2_snn <- selected_a_2_snn_temp - diag(nrow=n, ncol=n)
```

```{r}
isSymmetric(as.matrix(selected_a_2_snn))
```

```{r}
library(proxyC)
# ------- limitation of nodes degrees SYMMETRICS-------
print(sum(colZeros(selected_a_2_snn)))
for (i in 1:n){
  to_delete <- order(selected_a_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_a_2_snn[,i][to_delete] <- integer(n-ord)
  selected_a_2_snn[i,][to_delete] <- integer(n-ord)
}
print(sum(colZeros(selected_a_2_snn)))
```

```{r, eval=FALSE}
# ------- Enhance shared edges (may want to repeat multiple times) -------
library(Matrix)

# Method 2 (better)
mutual = matrix(0,n,n)

for (i in 1:n){
    mutual[i,] <- selected_a_2_snn[i,] & selected_a_2_snn[,i] 
}
nnzero(mutual)

selected_a_2_snn_old <- selected_a_2_snn
for (i in 1:n){
    selected_a_2_snn[i,] <- selected_a_2_snn_old[i,]+mutual[,i]
}
```

## Plot and save graphs

```{python}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["../../graphs/kidney/MNP/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_bench.gexf"])

G = nx.from_numpy_matrix(r.selected_a_2_snn)
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["../../graphs/kidney/MNP/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_bench.png"])
plt.savefig(file_name, bbox_inches='tight')
```

```{r}
knitr::include_graphics(py$file_name)
```

## Functions

```{r, eval=FALSE}
# ------- limitation of nodes degrees UNSYMMETRIC -------
print(sum(colZeros(selected_a_2_snn)))
for (i in 1:n){
  to_delete <- order(selected_a_2_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  selected_a_2_snn[,i][to_delete] <- integer(n-ord)
}
print(sum(colZeros(selected_a_2_snn)))
```

```{r, eval=FALSE}
# ------- Enhance shared edges (may want to repeat multiple times) -------
library(Matrix)

# Method 1
selected_a_2_snn_old <- selected_a_2_snn
for (i in 1:n){
    selected_a_2_snn[i,] <- selected_a_2_snn_old[i,]+selected_a_2_snn_old[,i]
}
```

```{python, eval=False}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

plotsavegraphs <- function(name, fdata) {

  id_type, type = int(r.id_type)-1, r.type
  n = int(r.n)
  k = int(r.k)
  ord = int(r.ord)
  dim = int(r.dim)

  file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_bench.gexf"])

  G = nx.from_numpy_matrix(r.selected_a_2_snn)
  nx.write_gexf(G, file_name)

  G = nx.read_gexf(file_name)
  pos = nx.spring_layout(G)
  plt.cla()
  nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
  nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

  file_name = ''.join(["../../graphs/kidney/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "_bench.png"])
  plt.savefig(file_name, bbox_inches='tight')
}
```
