---
title: "R Notebook"
output: html_notebook
---
takes QA clustered graph:   QA_pruned_clustered
takes Seurat object:        selected_b              (from "Data_subsampling" notebook, original graph)
takes Seurat object:        selected_b_2            (from "Data_subsampling" notebook, original graph)
takes Seurat object:        selected_b_2_pruned     (from "Data_subsampling" notebook, pruned graph)
# Libraries
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(Seurat)
library(ggplot2)
library(bspec)
library(sctransform)
library(cowplot)
library(gridExtra)
library(dplyr)
library(patchwork)
library(sctransform)
library(glmGamPoi)
library(philentropy)
library(proxy)
library(cluster)
library(Rfast)
```

# Get clustered-pruned graph back from QA
```{r setup}
library(reticulate)
virtualenv_create("scrna_proj")
# py_install(c("networkx","matplotlib"), envname = "scrna_proj")
use_virtualenv("scrna_proj")
```

```{python}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt
```

```{python}
name_pruned_clustered = "964_nodes_pruned/sample_number1.gexf"
QA_pruned_clustered = nx.read_gexf(''.join(["../../dataIn/kidney/Archive/", name_pruned_clustered]))
QA_pruned_clustered = nx.read_gexf(''.join(["../../graphs_multi_samples/", "sample_number0.gexf"]))

colors2 = [y[sorted(y.keys())[-1]] for x,y in QA_pruned_clustered.nodes(data=True)]
```

```{r}
colors2 = py$colors2
colors2 = unlist(colors2)
leng = dim(GetAssayData(selected_b_2))[2]

colors_vec <- integer(leng)
colors_vec[!!pruned] <- colors2+2

selected_b <- AddMetaData(selected_b, metadata=colors_vec, col.name="QA_pruning_clusters")
selected_b_2 <- AddMetaData(selected_b_2, metadata=colors_vec, col.name="QA_pruning_clusters")
selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=colors2, col.name="QA_pruning_clusters")
```

# Check clustering performance with the pruned graphs
```{r, eval=FALSE}
# DimPlot(selected_b_2_pruned, label = TRUE, label.size = 3, group.by="seurat_clusters") #+ NoLegend()
DimPlot(selected_b_2_pruned, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
DimPlot(selected_b_2_pruned, reduction = "umap", group.by="QA_pruning_clusters", label = TRUE)
```

```{r, eval=FALSE}
selected_2_pruned_new_umap <- RunUMAP(selected_b_2_pruned, dim=1:15)
DimPlot(selected_2_pruned_new_umap, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
DimPlot(selected_2_pruned_new_umap, reduction = "umap", group.by="QA_pruning_clusters", label = TRUE)
```

```{r, eval=FALSE}
selected_2_pruned_new_umap <- FindClusters(selected_2_pruned_new_umap, verbose = FALSE, resolution = 0.35, algorithm = 1)
DimPlot(selected_2_pruned_new_umap, reduction = "umap", group.by="seurat_clusters", label = TRUE)
```

```{r}
# ------- do kmeans clustering -------
km.out <- kmeans(selected_b_2_pruned@assays$SCT@data %>% as.matrix %>% t, centers=5, nstart=3)
selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=km.out$cluster, col.name="kmeans")
```

```{r}
my_cols <- c('#003366','#00cc99','#cc9900','#ff0066','#6699ff','#E6C122','#000195','#B95FBB','#28CECA','#ff9a36'
             ,'#2FF18B','#aeadb3','#CCB1F1','#D4D915','#A4DFF2','#4B4BF7')

DimPlot(selected_b_2_pruned, reduction = "umap", group.by="kmeans", cols=my_cols[1:5]) # + NoLegend()
DimPlot(selected_b_2_pruned, reduction = "umap", group.by="QA_pruning_clusters", cols=my_cols[1:5]) # + NoLegend()
DimPlot(selected_b_2_pruned, reduction = "umap", group.by="seurat_clusters", cols=my_cols[1:5]) # + NoLegend()
DimPlot(selected_b_2_pruned, group.by="celltype",repel = TRUE, label = TRUE, label.size = 3) #+ NoLegend()
```

# Benchmarks
## Index
### 1.Active Single
```{r}
library(fossil)

cell_type <- selected_b_2_pruned[["celltype"]][,1]
cell_kmeans <- selected_b_2_pruned[["kmeans"]][,1]
cell_qa <- selected_b_2_pruned[["QA_pruning_clusters"]][,1] + 1
cell_seurat <- as.numeric(as.vector(selected_b_2_pruned[["seurat_clusters"]][,1])) + 1

sort(table(cell_type))
sort(table(cell_kmeans))
sort(table(cell_qa))
sort(table(cell_seurat))
kmeans_order <- as.numeric(order(table(cell_kmeans)))
qa_order <- as.numeric(order(table(cell_qa)))
seurat_order <- as.numeric(order(table(cell_seurat)))
```

```{r}
cell_type <- selected_b_2_pruned[["celltype"]][,1]
size <- length(cell_type)
tcell_type <- vector(mode="character", length=size)

for (i in 1:size) {
  tcell_type[i] <- switch(cell_type[i], "Mast cell"=1, "CD8 T cell"=2, "NKT cell"=3, "NK cell"=4, "CD4 T cell"=5)
}
tcell_type <- as.numeric(tcell_type)
sort(table(tcell_type))
```

```{r}
size <- length(cell_type)
tcell_kmeans <- vector(mode="numeric", length=size)
tcell_qa <- vector(mode="numeric", length=size)
tcell_seurat <- vector(mode="numeric", length=size)

for (i in 1:size) {
  tcell_kmeans[i] <- switch(cell_kmeans[i], kmeans_order[1], kmeans_order[2], kmeans_order[3], kmeans_order[4], kmeans_order[5])
  tcell_qa[i]     <- switch(cell_qa[i], qa_order[1], qa_order[2], qa_order[3], qa_order[4], qa_order[5])
  tcell_seurat[i] <- switch(cell_seurat[i], seurat_order[1], seurat_order[2], seurat_order[3], seurat_order[4], seurat_order[5])
}
```

```{r}
rand.index(tcell_type, tcell_type)
adj.rand.index(tcell_type, tcell_type)

rand.index(tcell_kmeans, tcell_type)
adj.rand.index(tcell_kmeans, tcell_type)

rand.index(tcell_qa, tcell_type)
adj.rand.index(tcell_qa, tcell_type)

rand.index(tcell_seurat, tcell_type)
adj.rand.index(tcell_seurat, tcell_type)
```
### 1.Active Multi
```{python}
colors = []
for i in range(0,15):
  print(i)
  ex_number = str(i)
  QA_output_name = "sample_number" + ex_number + ".gexf"
  # name_pruned_clustered = "964_nodes_pruned/sample_number1.gexf"
  QA_clusters = nx.read_gexf(''.join(["../../dataIn/kidney/bench_3/first_3/", QA_output_name]))
  # QA_clusters = nx.read_gexf(''.join(["../../graphs_multi_samples/", QA_output_name]))
  # QA_pruned_clustered = nx.read_gexf(''.join(["../../dataIn/kidney/", name_pruned_clustered]))
  color = [y[sorted(y.keys())[-1]] for x,y in QA_clusters.nodes(data=True)]
  colors.append(color)
```

```{r}
colors <- py$colors

ref_rand <- c()
ref_adj_rand <- c()
km_rand <- c()
km_adj_rand <- c()
qa_rand <- c()
qa_adj_rand <- c()
seu_rand <- c()
seu_adj_rand <- c()

kmean_data <- selected_b_2_pruned@assays$SCT@data %>% as.matrix %>% t

for (i in c(1:15)) {
  print(i)
  color <- colors[i]
  color <- unlist(color)
  selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=color, col.name="QA")
  km.out <- kmeans(kmean_data, centers=5, nstart=1)
  selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=km.out$cluster, col.name="kmeans")
  
  cell_kmeans <- selected_b_2_pruned[["kmeans"]][,1]
  cell_qa <- selected_b_2_pruned[["QA"]][,1] + 1
  
  kmeans_order <- as.numeric(order(table(cell_kmeans)))
  qa_order <- as.numeric(order(table(cell_qa)))
  
  size <- length(cell_type)
  tcell_kmeans <- vector(mode="numeric", length=size)
  tcell_qa <- vector(mode="numeric", length=size)
  tcell_seurat <- vector(mode="numeric", length=size)
  
  for (i in 1:size) {
    tcell_kmeans[i] <- switch(cell_kmeans[i], kmeans_order[1], kmeans_order[2], kmeans_order[3], kmeans_order[4], kmeans_order[5])
    tcell_qa[i]     <- switch(cell_qa[i], qa_order[1], qa_order[2], qa_order[3], qa_order[4], qa_order[5])
    tcell_seurat[i] <- switch(cell_seurat[i], seurat_order[1], seurat_order[2], seurat_order[3], seurat_order[4], seurat_order[5])
  }
  
  ref_rand <- c(ref_rand, rand.index(tcell_type, tcell_type))
  # ref_adj_rand <- c(ref_adj_rand, adj.rand.index(tcell_type, tcell_type))
  
  km_rand <- c(km_rand, rand.index(tcell_kmeans, tcell_type))
  # km_adj_rand <- c(km_adj_rand, adj.rand.index(tcell_kmeans, tcell_type))
  
  qa_rand <- c(qa_rand, rand.index(tcell_qa, tcell_type))
  # qa_adj_rand <- c(qa_adj_rand, adj.rand.index(tcell_qa, tcell_type))
  
  seu_rand <- c(seu_rand, rand.index(tcell_seurat, tcell_type))
  # seu_adj_rand <- c(seu_adj_rand, adj.rand.index(tcell_seurat, tcell_type))
  
}

clipr::write_clip(ref_rand)
clipr::write_clip(qa_rand)
clipr::write_clip(km_rand)
clipr::write_clip(seu_rand)
# 
# clipr::write_clip(ref_adj_rand)
# clipr::write_clip(km_adj_rand)
# clipr::write_clip(qa_adj_rand)
# clipr::write_clip(seu_adj_rand)

max_index_qa <- max(qa_rand)
clipr::write_clip(max_index_qa)
```

```{r}
kmeans_data <- selected_b_2_pruned@assays$SCT@data %>% as.matrix %>% t
size <- length(cell_type)

km_index_count <- c()

for (i in 1:1) {
  km_index <- 0
  km_index_list <- c()
  iter <- 0

  print(i)
  
  while (km_index < max_index_qa && iter < 1000) {
    iter <- iter + 1
    print(iter)
    
    km.out <- kmeans(kmeans_data, centers=5, nstart=1)
    selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=km.out$cluster, col.name="kmeans")
    
    cell_kmeans <- selected_b_2_pruned[["kmeans"]][,1]
    kmeans_order <- as.numeric(order(table(cell_kmeans)))
    tcell_kmeans <- vector(mode="numeric", length=size)
    
    for (i in 1:size) {
      tcell_kmeans[i] <- switch(cell_kmeans[i], kmeans_order[1], kmeans_order[2], kmeans_order[3], kmeans_order[4], kmeans_order[5])
    }
    
    km_index <- rand.index(tcell_kmeans, tcell_type)
    km_index_list <- c(km_index_list, km_index)

  }
  write.csv(km_index_list,file=paste('./kmean_index_stats_2/', as.character(i),'.csv'),row.names=F)
  km_index_count <- c(km_index_count, iter)
}

clipr::write_clip(km_index_count)
```


## 2.Silhouette
### 2.Active Multi
```{python}
colors = []
for i in range(0,15):
  print(i)
  ex_number = str(i)
  QA_output_name = "sample_number" + ex_number + ".gexf"
  QA_clusters = nx.read_gexf(''.join(["../../dataIn/kidney/bench_3/first_4/", QA_output_name]))
  # QA_clusters = nx.read_gexf(''.join(["../../graphs_multi_samples/", QA_output_name]))
  color = [y[sorted(y.keys())[-1]] for x,y in QA_clusters.nodes(data=True)]
  colors.append(color)
```

```{r}
sc_dist_fast <- Dist(selected_b_2_pruned@assays$SCT@data %>% as.matrix %>% t)

colors <- py$colors
res_qa <- c()

for (i in 1:15) {
  print(i)
  color <- colors[i]
  color <- unlist(color)
  selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=color, col.name="QA")
  df_silhouette_results_QA <- silhouette(selected_b_2_pruned[["QA"]][,1], sc_dist_fast)
  res_qa <- c(res_qa, mean(df_silhouette_results_QA[,3]))
}

max_res_qa = max(res_qa)
clipr::write_clip(max_res_qa)
clipr::write_clip(res_qa)
```

```{r, eval=FALSE}
kmeans_data <- selected_b_2_pruned@assays$SCT@data %>% as.matrix %>% t

res_km <- c()

for (i in 1:15) {
  print(i)
  km.out <- kmeans(kmeans_data, centers=5, nstart=1)
  selected_b_2_pruned <- AddMetaData(selected_b_2_pruned, metadata=km.out$cluster, col.name="kmeans")
  df_silhouette_results_kmeans <- silhouette(selected_b_2_pruned[["kmeans"]][,1], sc_dist_fast)
  res_km <- c(res_km, mean(df_silhouette_results_kmeans[,3]))
}

clipr::write_clip(res_km)
```

```{r, eval=FALSE}
res_se <- c()

for (i in 1:15) {
  print(i)
  df_silhouette_results_seurat <- silhouette(as.numeric(as.vector(selected_b_2_pruned[["seurat_clusters"]][,1])), sc_dist_fast)
  res_se <- c(res_se, mean(df_silhouette_results_seurat[,3]))
}

clipr::write_clip(res_se)
```

### 2.No-active
```{r, eval=FALSE}

colors = py$colors
colors = unlist(colors)
selected_a_2<- AddMetaData(selected_a_2, metadata=colors, col.name="QA")
  
pbmc3k_QA <- selected_a_2
sc_dist_fast <- Dist(pbmc3k_QA@assays$SCT@data %>% as.matrix %>% t %>% as.data.frame)

for (i in 1:3) {
  km.out <- kmeans(pbmc3k_QA@assays$SCT@data %>% as.matrix %>% t %>% as.data.frame, centers=5, nstart=3)
  pbmc3k_QA <- AddMetaData(pbmc3k_QA, metadata=km.out$cluster, col.name="kmeans")
  
  # write.table(data.frame(QA_stats[i]), paste('./fpc/QA_benchmark', ex_number, '.csv'), append= T, sep=',')
  # print(as.vector(names(QA_stats))[i])
  
  df_silhouette_results_kmeans <- silhouette(pbmc3k_QA[["kmeans"]][,1], sc_dist_fast)
  df_silhouette_sum_kmeans <- sum(df_silhouette_results_kmeans[,"sil_width"])
  summary(df_silhouette_results_kmeans)
  
  cat("\n")
  
  df_silhouette_results_QA <- silhouette(pbmc3k_QA[["QA"]][,1], sc_dist_fast)
  df_silhouette_sum_QA <- sum(df_silhouette_results_QA[,"sil_width"])
  summary(df_silhouette_results_QA)
  
  cat("\n")
  
  df_silhouette_results_seurat <- silhouette(as.numeric(as.vector(pbmc3k_QA[["seurat_clusters"]][,1])), sc_dist_fast)
  df_silhouette_sum_seurat <- sum(df_silhouette_results_seurat[,"sil_width"])
  summary(df_silhouette_results_seurat)
  
  cat("\n")
  
  c(df_silhouette_sum_kmeans, df_silhouette_sum_QA, df_silhouette_sum_seurat)
}
```

## 3.Kmeans in loop to reach QA Seurat accuracy 
```{r, eval=FALSE}
################### Silhouette & rand index ###################
res_km <- c()
res_mkm <- c()
iter <- 0
meankmean <- 0
kmeans_data <- pbmc3k_QA@assays$SCT@data %>% as.matrix %>% t

for (i in 1:2) {
  meankmean <- 0
  iter <- 0
  res_km <- 0
  print(i)
  while (meankmean < max_res_qa) {
    iter <- iter + 1
    print(iter)
    km.out <- kmeans(kmeans_data, centers=5, nstart=1)
    pbmc3k_QA <- AddMetaData(pbmc3k_QA, metadata=km.out$cluster, col.name="kmeans")
    df_silhouette_results_kmeans <- silhouette(pbmc3k_QA[["kmeans"]][,1], sc_dist_fast)
    meankmean <- mean(df_silhouette_results_kmeans[,3])
    res_km <- c(res_km, meankmean)
  }
  # write.csv(res_km,file=paste('./kmean_stats/', as.character(i),'.csv'),row.names=F)
  res_mkm <- c(res_mkm, iter)
}

# clipr::write_clip(res_km)
clipr::write_clip(res_mkm)
# print(iter)
```

```{r, eval=FALSE}
hist(res_km, breaks=iter)
```