---
title: "R Notebook"
output: html_notebook
---

# Libraries
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(Seurat)
library(ggplot2)
library(bspec)
library(sctransform)
library(cowplot)
library(gridExtra)
library(dplyr)
library(patchwork)
library(sctransform)
library(glmGamPoi)
```

# Get clustered-pruned graph back from QA
takes QA clustered graph:   QA_pruned_clustered
takes Seurat object:        pbmc3k_QA_pd        (from "Data_subsampling" notebook, original graph)
takes Seurat object:        pbmc3k_QA_pruned    (from "Data_subsampling" notebook, pruned graph)
```{python}
name_pruned_clustered = "239_cqm_graph_snn_k5_dim15_g0005_trimmed_15.gexf"
QA_pruned_clustered = nx.read_gexf(''.join(["./dataIn/", name_pruned_clustered]))

colors2 = [y[sorted(y.keys())[-1]] for x,y in QA_pruned_clustered.nodes(data=True)]
```

```{r}
colors2 = py$colors2
colors2 = unlist(colors2)
leng = dim(GetAssayData(pbmc3k_QA_pd))[2]

colors_vec <- integer(leng)
colors_vec[!!pruned] <- colors2+2

pbmc3k_QA_pd <- AddMetaData(pbmc3k_QA_pd, metadata=colors_vec, col.name="QA_pruning_clusters")
pbmc3k_QA_pruned <- AddMetaData(pbmc3k_QA_pruned, metadata=colors2, col.name="QA_pruning_clusters")
```

# Check clustering performance with the pruned graphs
```{r}
pbmc3k_QA_pruned <- RunUMAP(pbmc3k_QA_pruned, dim=1:15)
DimPlot(pbmc3k_QA_pruned, reduction = "umap", group.by="QA_pruning_clusters", label = TRUE)
```

```{r}
pbmc3k_QA_pruned <- FindClusters(pbmc3k_QA_pruned, verbose = FALSE, resolution = 0.8, algorithm = 1)
DimPlot(pbmc3k_QA_pruned, reduction = "umap", group.by="seurat_clusters", label = TRUE)
```

# Check clustering performance with the original graphs
```{r}
pbmc3k_QA_pd <- RunUMAP(pbmc3k_QA_pd, dim=1:15)
DimPlot(pbmc3k_QA, cells=!!pruned, reduction = "umap", group.by="QA_pruning_clusters", label = TRUE)
```

```{r}
pbmc3k_QA_pd <- FindClusters(pbmc3k_QA_pd, verbose = FALSE, resolution = 0.8, algorithm = 1)
DimPlot(pbmc3k_QA_pd, cells=!!pruned, reduction = "umap", group.by="seurat_clusters", label = TRUE)
```

```{r}
DimPlot(pbmc3k_QA_pd, reduction = "umap", group.by="seurat_clusters", label = TRUE)
```


## Generate SNN Graph (second version)
takes Seurat object: takes rc_pbmc3k with 2700 cells (from "Assess_QA_clusters" notebook) 
```{r}
n = ncol(rc_pbmc3k)
dim(rc_pbmc3k)

type = c("_", "_trimmed_", "_negedges_", "_trimmed_negedges_")
id_type = 2
dim = 15
k = 5
coff = 0 #1/15
ord = 15

rc_pbmc3k <- FindNeighbors(rc_pbmc3k, reduction = "ref.spca", dims = 1:dim, k.param=k, compute.SNN=TRUE) #prune.SNN=coff

rc_pbmc3k_snn <- rc_pbmc3k@graphs[["SCT_snn"]]

dim(rc_pbmc3k_snn)
rc_pbmc3k_snn_temp <- rc_pbmc3k_snn
rc_pbmc3k_snn <- rc_pbmc3k_snn_temp - diag(n)
remove(rc_pbmc3k_snn_temp)

for (i in 1:n){
  to_delete <- order(rc_pbmc3k_snn[,i], decreasing = TRUE)[seq(ord+1,n,1)]
  rc_pbmc3k_snn[,i][to_delete] <- integer(n-ord)
  rc_pbmc3k_snn[i,][to_delete] <- integer(n-ord)
}
```

```{r setup}
library(reticulate)
virtualenv_create("scrna_proj")
# py_install(c("networkx","matplotlib"), envname = "scrna_proj")
use_virtualenv("scrna_proj")
```

```{python}
import numpy as np
import networkx as nx
from matplotlib import pyplot as plt

id_type, type = int(r.id_type)-1, r.type
n = int(r.n)
k = int(r.k)
ord = int(r.ord)
dim = int(r.dim)

file_name = ''.join(["./graphs/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "v2.gexf"])

G = nx.from_numpy_matrix(r.rc_pbmc3k_snn)
nx.write_gexf(G, file_name)

G = nx.read_gexf(file_name)
pos = nx.spring_layout(G)
plt.cla()
nx.draw_networkx_nodes(G, pos, node_size=10, nodelist=G.nodes)
nx.draw_networkx_edges(G, pos, edgelist=G.edges, style='solid', alpha=0.5, width=1)

file_name = ''.join(["./graphs/", str(n), "_graph_snn", "_k", str(k), "_dim", str(dim), type[id_type], str(ord), "v2.png"])
plt.savefig(file_name, bbox_inches='tight')
```

```{python}
import networkx as nx
# QA_output_name = "1024_graph_snn_k5_dim15_gf0.05_trimmed_5_out.gexf"
QA_output_name_v2 = "512_cqm_graph_snn_k5_dim15_g0005_trimmed_15v2.gexf"

QA_clusters_v2 = nx.read_gexf(''.join(["./dataIn/", QA_output_name_v2]))

# ------- CHOSE THE CORRECT OPTION BASED ON THE EXPORTED FORMAT -------
colors_v2 = [y[sorted(y.keys())[-1]] for x,y in sorted(QA_clusters_v2.nodes(data=True))]
colors_v2 = [y[sorted(y.keys())[-1]] for x,y in QA_clusters_v2.nodes(data=True)]
```

### Merge MetaData
```{r}
colors_v2 = py$colors_v2
colors_v2 = unlist(colors_v2)
rc_pbmc3k <- AddMetaData(rc_pbmc3k, metadata=colors_v2, col.name="QA")
DimPlot(rc_pbmc3k, reduction = "pca", group.by="QA")
```

```{r}
rc_pbmc3k <- FindClusters(rc_pbmc3k, verbose = FALSE, resolution = 0.8, algorithm = 1)
rc_pbmc3k <- RunUMAP(rc_pbmc3k, dim=1:15)

png(file="./output/clusters_QAv2.png")
DimPlot(rc_pbmc3k, reduction = "umap", group.by="QA") # + NoLegend()
dev.off()

png(file="./output/clusters_Clasic.png")
DimPlot(rc_pbmc3k, reduction = "umap", group.by="seurat_clusters") # + NoLegend()
dev.off()

DimPlot(rc_pbmc3k, reduction = "umap", group.by="QA") # + NoLegend()
DimPlot(rc_pbmc3k, reduction = "ref.umap", group.by="seurat_clusters") # + NoLegend()
```